### 2014-03-12 paper/designspace.tex
integrate tovi comments

\subsection{Types of Tubes}

Tubes can come in four types: open, return, semi-closed, and fully enclosed.  Each of these types offers distinct interaction capabilities (see Figure \ref{fig:tubespace}).

Open tubes originate from the system side and connect the user side, with both ends of the tube open.  This type of tube may be used to create, for example, capacitive sensors: an open tube filled with conductive paint can be connected to a sensing platform (e.g., Arduino) on the system side, while a user can touch the uncapped other end of the tube.  Using Swept Frequency Capacitive Sensing \cite{Sato-touche} or other techniques, a user's touch of the open end can be sensed.  An open tube can also be used for output, for example by creating in-air vortices as in \cite{Sodhi-aireal}.

@@

Semi-closed tubes are open at the system end (for control of the enclosed medium) and closed at the user end.  We believe this closed interface is most interesting when it is fabricated from a mobile material: for example, a series of tubes terminated in thin rubber membranes on the user side can be actuated by an air pump to create haptic feedback.  Without a printer capable of fabricating flexible material, a maker could affix a balloon to an open tube's end to behave similarly; another possibility is to use semi-closed tubes as audio-generating resonance chambers.

While possible to create, a tube which is open on the user side and closed on the system side is outside our focus on computer-mediated interaction, and we therefore do not discuss these tubes.

A fully enclosed tube has no openings on either the system side or the user side.  Fully enclosed tubes can be used as resonance chambers (e.g., for object identification), or as air bubbles (e.g., as used in \cite{Willis-printedoptics} for internal display).  Their physical design space is very limited, as any support material required to create their internal geometry cannot be accessed for removal.

@@

``Gas'' comprises all compressible fluids.  Use of fluid pressure inside tubes can create haptic feedback at semi-closed interfaces, or the gases can be used as carriers for scents or fog.  As in \cite{Slyper-pressure}, structures can be engineered to change in air pressure when manipulated correctly (e.g., a spiral that changes pressure when twisted, but not pressed), and thus fluid pressure can also be used as an input.

@@

Tubes need not have hollow centers: in the case where routed tubes are filled with solid material---in particular, a solid material different from the model material---, interactions such as those in \cite{Willis-printedoptics} are possible.

@@

Tube topology enables different types of interactions.

Splitting or mixing tubes offer flexibility in output.  If a maker wished to create a painting device, she might wish to have two system-side tubes feeding in primary-colored red and blue paints which mix in varying ratios, allowing their pigments to combine before purple exits from the device (see Figure \ref{fig:tubespace}).  Splitting can also be useful, for example if our maker wants red paint output in two locations from her painting device, she could have one system-side tube, but split the tube into two (see Figure \ref{fig:tubespace}).

Star and tree topologies are extensions of the splitting and mixing primitives.  Using a star topology in which the tubes were filled with conductive paint, we created a toy with several touch-sensitive areas, see Figure \ref{fig:toy}.

@@

Tubes may emphasize either their exterior features (connection points) or their interior paths.  These two features lead to different kinds of interfaces.  An example interface that focuses on the exterior connection points is the touch sensitive toy in Figure \ref{fig:toy}, where tubes must exit the toy at the eyes, ears, tail, etc.  An interface focused on the internal path of the tube is the neon sign in Figure \ref{fig:neon}: output is based on the shape of the tube.

@@

\valkyrie{this section includes related work.  is that ok?  it's in the table, and I think we should cover the related input techniques here rather than in the designated related work section (which I think is more suited to fabrication and routing stuff).}

>>>>

\subsection{Types of Tubes}\tovi{Maybe rename types to 
"openings"?}

Tubes can come in four types: open, return, semi-closed, and fully enclosed.  Each of these types offers distinct interaction capabilities (see Figure \ref{fig:tubespace}).\tovi{Need to clarify if the type is defined by the 3D model at the time it 
is printed, or by any alternations made after the print. For example, 
if I print semiclosed, fill with water, then close it manually with a lit, 
is it a semclsoed tube or a fully enclosed tube?}

Open tubes originate from the system side and connect the user side, with both ends of the tube open. \tovi{Not clear what 
"system side and user 
site means.}  This type of tube may be used to create, for example, capacitive sensors: an open tube filled with conductive paint can be connected to a sensing platform (e.g., Arduino) on the system side, while a user can touch the uncapped other end of the tube.  Using Swept Frequency Capacitive Sensing \cite{Sato-touche} or other techniques, a user's touch of the open end can be sensed.  An open tube can also be used for output, for example by creating in-air vortices as in \cite{Sodhi-aireal}.

@@

Semi-closed tubes are open at the system end (for control of the enclosed medium) and closed at the user end.  We believe \tovi{Reword ("we believe" is strange)} this closed interface is most interesting when it is fabricated from a mobile material \tovi{Do you mean mobile materials or flexible material?}\valkyrie{I think mobile... we can cap them with solid pieces that can be blown around by air, for example.  how do I make this clear?}: for example, a series of tubes terminated in thin rubber membranes on the user side can be actuated by an air pump to create haptic feedback.  Without a printer capable of fabricating flexible material, a maker could affix a balloon to an open tube's end to behave similarly; another possibility is to use semi-closed tubes as audio-generating resonance chambers.

While possible to create, a tube which is open on the user side and closed on the system side is outside our focus on computer-mediated interaction, and we therefore do not discuss these tubes. \tovi{Reword, and may not be necceary}

A fully enclosed tube has no openings on either the system side or the user side.  Fully enclosed tubes can be used as resonance chambers (e.g., for object identification), or as air bubbles (e.g., as used in \cite{Willis-printedoptics} for internal display). \tovi{used as a container for water 
or other particles that would 
otherwise fall out?}  Their physical design space is very limited, as any support material required to create their internal geometry cannot be accessed for removal.

@@

``Gas'' comprises all compressible fluids.  Use of fluid pressure inside tubes can create haptic feedback at semi-closed interfaces, or the gases can be used as carriers for scents or fog.  As in \cite{Slyper-pressure}, structures can be engineered to change in air pressure when manipulated correctly (e.g., a spiral that changes pressure when twisted, but not pressed), and thus fluid pressure can also be used as an input. \tovi{I realize "fluid" pressure is 
technically correct, but might 
confuse readers, since this is 
the gas pararaph.}

@@

\tovi{Again, this raises the question of how we are applying the design 
space - is it based on its properties when it is printed, or based on 
any post-print modifications}Tubes need not have hollow centers: in the case where routed tubes are filled with solid material---in particular, a solid material different from the model material---, interactions such as those in \cite{Willis-printedoptics} are possible.

@@

Tube topology enables different types of interactions. \tovi{How about "newwork 
topologies", since this 
applies to groups of tubes.
}

Splitting or mixing tubes offer flexibility in output.  If a maker wished to create a painting device, she might wish to have two system-side tubes feeding in primary-colored red and blue paints which mix in varying ratios, allowing their pigments to combine before purple exits from the device (see Figure \ref{fig:tubespace}).  Splitting can also be useful, for example if our maker wants red paint output in two locations from her painting device, she could have one system-side tube, but split the tube into two (see Figure \ref{fig:tubespace}).\tovi{How about multiple in/
multiple out (in contrast to 
branching/splitting which is 
single in multiple out)
} \tovi{This seciton should refer to the 
possibilities, not to what we 
actually did.}

Star and tree topologies are extensions of the splitting and mixing primitives.  Using a star topology in which the tubes were filled with conductive paint, we created a toy with several touch-sensitive areas, see Figure \ref{fig:toy}. \tovi{May want star, tree added to 
your figure
}

@@

Tubes may emphasize either their exterior features (connection points) or their interior paths.  These two features lead to different kinds of interfaces.  An example interface that focuses on the exterior connection points is the touch sensitive toy in Figure \ref{fig:toy}, where tubes must exit the toy at the eyes, ears, tail, etc.  An interface focused on the internal path of the tube is the neon sign in Figure \ref{fig:neon}: output is based on the shape of the tube. \tovi{This is not consistent with the 
fourth row of your table. Not sure 
this paragraph is needed.
}

@@

\valkyrie{this section includes related work.  is that ok?  it's in the table, and I think we should cover the related input techniques here rather than in the designated related work section (which I think is more suited to fabrication and routing stuff).} \tovi{Yes, related work here is ok, if it 
doesnt belong in the realted 
work section. Agreed that 
seciton should be highler level 
discussion of fabrication and 
routing.
}
